### 2024-06-02 thesis/input_files/analysis.tex
June 2nd 2024

The resulting RMSE is 30.59.
What can be concluded, is that multiple linear regression is capable of catching the daily seasonality. Nevertheless, it cannot catch the range of the price series properly.

\subsection{Trigonometric seasonality Box-Cox transformation ARMA errors trend and seasonal components}
Next, we tried with the autoregressive approach. Unfortunately, AR, ARIMA and SARIMA models did not perform as expected, their output was slightly better than the one of linear regression. This is probably due to the fact that, the data considered entails two kinds of seasonalities, while ARIMA models can only handle one at a time. We remind the reader, that the electricity load time series involves both daily and weekly seasonalities. Hence, the need for a more advanced time series model. The Tbats \cite{de2011forecasting} model is a forecasting method capable of handling complex patterns in the data. Its name stands for trigonometric seasonality, Box-Cox transformation, ARMA errors, trend and seasonal components. 
Tbats forecast is visualized in Figure \ref{fig:tbats_price}, meanwhile its RMSE is 15.08.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/tbats_price.png}
    \caption{Tbats prediction}
    \label{fig:tbats_price}
\end{figure}
From the plot we see that Tbats is capable of catching the lows and average trend, conversely it has some difficulties handling the price peaks.
\subsection{Prophet}
Following, the prophet model has been considered. 
We get started by considering the base implementation. In such setting, prophet takes as input the time series object and learns its data generating process.
This method achieves a RMSE of 23.96, its prediction is visualized in Figure \ref{fig:prophet_price_1}.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/prophet_price_1.png}
    \caption{Prophet prediction}
    \label{fig:prophet_price_1}
\end{figure}
What can be seen is that prophet correctly models the average trend but does not model peaks and lows precisely. 
Next, a more complex model was trained. We added the weather temperature, the square of it and the categorical variable for holidays effect as regressors. Furthermore, we also applied a log transformation to the dependent variables. Doing so, RMSE went down to 10.29. Forecast is visualised in Figure \ref{fig:prophet_price2}.
% , moreover figure \ref{fig:prophet_price2.1} and figure \ref{fig:prophet_price2.2} break down the trend and the seasonalities respectively.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/prophet_price2.png}
    \caption{Prophet model\_2 prediction}
    \label{fig:prophet_price2}
\end{figure}

@@

\subsection{K-nearest neighbours}
Afterwards, K-nearest neighbours has been considered. In doing so, we cross validated the number of neighbours to get the best model instance. The forecast is visualised in Figure \ref{fig:knn_price}, RMSE is 12.54.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/knn_price.png}
    \caption{K-nearest neighbour regression}
    \label{fig:knn_price}
\end{figure}
What it can be said is that, K-nearest neighbour is capable of predicting load well by averaging past data.

\subsection{Support vector regression}
In applying support vector regression we used gridsearch crossvalidation to search for the best regularisation parameter $C$. Support vector regression achieves an RMSE of 23.24, for the prediction see Figure \ref{fig:svr_price}.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/svr_price.png}
    \caption{Support vector regression prediction}
    \label{fig:svr_price}
\end{figure}
Visually, we see that the SVR performs similar to multiple linear regression, as expected. Like multiple linear regression, SVR can model the daily seasonality but the point prediction is off in terms of highs and lows.

\subsection{Long short term memory}
We used the \href{https://pytorch.org}{torch} library in order to code our LSTM regressor.
Various hyperparameters combinations were tried during the tuning phase. The final architecture we set on follows
\begin{itemize}
    \item hidden\_size= 64
    \item num\_layers= 2
    \item output\_size= 1
    \item num\_epochs= 30
    \item learning\_rate= 0.001
    \item batch\_size= 32
    \item window\_size= 24
\end{itemize}
LSTM forecast is reported in Figure \ref{fig:lstm_price}, it achieves a RMSE of 9.1782
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/lstm_price.png}
    \caption{Long short term memory prediction}
    \label{fig:lstm_price}
\end{figure}

\subsection{Kernel ridge regression}
Subsequently, kernel ridge regression was considered. The kernel considered is the radial basis Gaussian function.
Cross validation was carried jointly over the RBF kernel bandwith and the regularisation constant.
The RMSE achieved is 9.86, Figure \ref{fig:krnridge_price} reports the prediction.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/krnridge_price.png}
    \caption{Kernel ridge prediction}
    \label{fig:krnridge_price}
\end{figure}
We can observe that, kernel ridge regression accurately models the electricity time series.

\subsection{Kernel support vector regression}
The last model we considered in this setting was the kernel support vector regression.
RMSE achieved with this method is 9.10, forecast is reported in Figure \ref{fig:krnsvr_price}.

@@

\subsection{Results}
This section reports the tables comparing the considered methods scores.
% in the context of electricity load forecasting.

@@

% quantile regressors
\subsection{Quantile regressors comparison}
Using the load data from \href{https://www.energy-charts.info/index.html?l=en&c=DE}{energy charts} for Germany and Switzerland, we proceeded to compare between quantile regression algorithms. In this study, we trained our models on the entire 2021 data and then tested them and measured their score on the 2022 data.
Notice, for kernel quantile regression (KQR), the kernel of choice in this setting is the absolute Laplacian. Additionally notice, the loss function utilized in this section is the normalized pinball loss. 
% normalized by the magnitude of the average load of each country.
Here, we built two models. In the first, the national load is forecasted by taking as predictor the following variables
\begin{itemize}
    \item Weather temperature
    \item Wind speed
\end{itemize}
Results for Germany are reported in table \ref{tab:energy_chart_de} and figure \ref{fig:DE_load_CI} while results for Switzerland can be found in table \ref{tab:energy_chart_ch} and figure \ref{fig:CH_load_CI}.

@@

    \begin{figure}[!ht]
        \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/DE_load_CI.png}}
        \caption[Probabilistic forecast for load in Germany]{Load 90\% confidence interval for Germany Energy charts (2022) data using KQR Laplacian. The black line is the observed path for the load. The 90\% confidence interval bands are plotted in green. Lower and upper red lines denote the 95\% and 5\% quantile forecast respectively}
        \label{fig:DE_load_CI}
    \end{figure}

    \begin{figure}[!ht]
        \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/CH_load_CI.png}}
        \caption[Probabilistic forecast for load in Switzerland]{Load 90\% confidence interval for Switzerland Energy charts data (2022) using KQR Laplacian. The black line is the observed path for the load. The 90\% confidence interval bands are plotted in green. Lower and upper red lines denote the 95\% and 5\% quantile forecast respectively}
        \label{fig:CH_load_CI}
    \end{figure}

Next, we extended the models to take into account the impact of two additional categorical variables
\begin{itemize}
    \item Is holiday: a binary variable for holidays, where holiday$=1$ and working day$=0$
    \item Day of week: an ordinal categorical variable corresponding to the day of the week, e.i.\ Monday$=0$,$\dots$, Sunday$=6$
\end{itemize}
Table \ref{tab:energy_chart_de_additional_predictors} reports the model scores on the German data while Table \ref{tab:energy_chart_ch_additional_predictors} is the one corresponding to the Swiss data.

@@

% now comment tables
What can be concluded from this first study is that kernel quantile regression equipped with the absolute Laplacian kernel outperformed almost always its contenders.

% kernel comparison
\subsection{Kernel function choice}
This section analyzes which kernel function best fits to the characteristics of the load data.
The kernel functions considered are: Gaussian RBF, absolute Laplacian, Matern 1.5, Matern 2.5, Linear, Periodic, Polynomial, Sigmoid, and Cosine. 
Details concerning the hyperparameter selection for the different kernels can be found in \href{https://scikit-learn.org/stable/modules/classes.html#module-sklearn.metrics.pairwise}{sklearn.metrics.pairwise} and \href{https://scikit-learn.org/stable/modules/classes.html#module-sklearn.gaussian_process}{sklearn.gaussian\_process}.
The pool of data for this study has been created by combining \href{https://zenodo.org/records/7907883}{SECURES-Met} data (predictors) \cite{Formayer2023} and the load data from \href{https://www.energy-charts.info/index.html?l=en&c=DE}{energy charts}.
SECURES-Met data consists of historical data up to the end of $2020$ while from 2021 onward, the data consists of forecasts modeled by the European Centre for Medium-Range Weather Forecasts (ECMWF).
Therefore, in this experimental study, we used the whole data of $2020$ as the training set and then tested our kernels on the $2021$ data.
Note that there are two kinds of predictions for data from $2021$ onward, one for each of the emission scenarios RCP$4.5$ and RCP$8.5$. In this study, we considered the more conservative RCP$4.5$ scenario data.

@@

\begin{table}[!ht]
    \centering
    \caption{Pinball loss kernel comparison for load in Switzerland (2021)}
    \label{tab:secures_met_ch}
    \begin{adjustbox}{width=\textwidth}
        \begin{tabular}{lllllllllll}
            \toprule
            Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
            \midrule
            0.1 & \textbf{0.018783} & 0.018988 & 0.019108 & 0.019257 & 0.019547 & 0.019952 & 0.018891 & 0.019654 & 0.021456 & 0.021921 \\
            0.2 & \textbf{0.030441} & 0.030668 & 0.030809 & 0.031028 & 0.031546 & 0.032158 & 0.030683 & 0.031857 & 0.034032 & 0.034629 \\
            0.3 & \textbf{0.038467} & 0.038864 & 0.039050 & 0.039285 & 0.039907 & 0.040657 & 0.038968 & 0.040075 & 0.042944 & 0.043393 \\
            0.4 & \textbf{0.043622} & 0.044186 & 0.044516 & 0.044706 & 0.045286 & 0.046153 & 0.044354 & 0.045506 & 0.048701 & 0.048977 \\
            0.5 & \textbf{0.046160} & 0.046792 & 0.047205 & 0.047450 & 0.048116 & 0.048951 & 0.046956 & 0.047891 & 0.051423 & 0.051896 \\
            0.6 & \textbf{0.045499} & 0.046133 & 0.046824 & 0.047177 & 0.047840 & 0.048667 & 0.046446 & 0.047496 & 0.051292 & 0.051894 \\
            0.7 & \textbf{0.041494} & 0.042044 & 0.042928 & 0.043371 & 0.044104 & 0.044926 & 0.042458 & 0.043565 & 0.047656 & 0.048275 \\
            0.8 & \textbf{0.033837} & 0.034128 & 0.034797 & 0.035325 & 0.036166 & 0.037055 & 0.034290 & 0.035533 & 0.039501 & 0.040007 \\
            0.9 & \textbf{0.021883} & 0.021871 & 0.022431 & 0.022682 & 0.023169 & 0.023730 & 0.022000 & 0.022811 & 0.025561 & 0.026019 \\
            \midrule
            CRPS & \textbf{0.035576} & 0.035964 & 0.036407 & 0.036698 & 0.037298 & 0.038028 & 0.036116 & 0.037154 & 0.040285 & 0.040779 \\
            \bottomrule
    \end{tabular}
\end{adjustbox}
    \end{table}

@@

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Austria (2021)}
\label{tab:secures_met_at}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
        \toprule
        Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
        \midrule
        0.1 & \textbf{0.024365} & 0.024592 & 0.024550 & 0.024611 & 0.024831 & 0.026853 & 0.025744 & 0.026004 & 0.027672 & 0.027816 \\
        0.2 & \textbf{0.040971} & 0.041406 & 0.041413 & 0.041487 & 0.041857 & 0.045007 & 0.043247 & 0.043720 & 0.045899 & 0.045879 \\
        0.3 & \textbf{0.052316} & 0.052969 & 0.052888 & 0.052973 & 0.053449 & 0.057880 & 0.055231 & 0.055446 & 0.058572 & 0.058454 \\
        0.4 & \textbf{0.058286} & 0.059018 & 0.058916 & 0.059078 & 0.059592 & 0.065770 & 0.061844 & 0.062495 & 0.066599 & 0.066335 \\
        0.5 & 0.060344 & 0.061100 & 0.061319 & 0.061541 & 0.062338 & 0.068197 & 0.063864 & 0.071731 & 0.069761 & 0.069574 \\
        0.6 & \textbf{0.058724} & 0.059507 & 0.059674 & 0.059930 & 0.060709 & 0.065828 & 0.062265 & 0.070269 & 0.067179 & 0.066970 \\
        0.7 & \textbf{0.053148} & 0.054189 & 0.054249 & 0.054372 & 0.054916 & 0.058548 & 0.055830 & 0.063015 & 0.059807 & 0.059419 \\
        0.8 & \textbf{0.042740} & 0.043368 & 0.043408 & 0.043510 & 0.043881 & 0.046017 & 0.044384 & 0.049813 & 0.047078 & 0.046662 \\
        0.9 & \textbf{0.026430} & 0.026583 & 0.026781 & 0.026817 & 0.026908 & 0.027050 & 0.026471 & 0.030279 & 0.028031 & 0.027986 \\
        \midrule
        CRPS & \textbf{0.046369} & 0.046970 & 0.047022 & 0.047146 & 0.047609 & 0.051239 & 0.048764 & 0.052530 & 0.052289 & 0.052122 \\
        \bottomrule
    \end{tabular}
\end{adjustbox}
\end{table}
From our tables, it can be concluded that the absolute Laplacian kernel is the one fitting best to the characteristics of load data.
Additionally, we can conclude that our results are in line with the ones published in \cite{he2017short}. In that study, similarly to what we did in this subsection, the authors carried out a comparitive study concerning the choice of kernels in KQR. Nevertheless notice, that the set of kernel we considered in our study is larger than the one presented in \cite{he2017short}.
Their paper showed evidence of the superiority of the Gaussian RBF among their set of kernel functions. Analogously, we can see from Tables \ref{tab:secures_met_de}, \ref{tab:secures_met_ch} and \ref{tab:secures_met_at} that the Matern kernels are the best in terms of pinball loss.
The Periodic equipped with period $p=24$ shows good performance. 
After those kernels, we have the Linear and Polynomial kernel.
The worst among all kernels considered are the Cosine and the Sigmoid.
% , which is better suited for binary classification tasks. 
Finally, given that the features dimension is greater than one we have that the Absolute Laplacian and the Matern 0.5 kernels differ. The former kernel is better than the latter and this comes from their distance function. This is because the Manhattan distance is more robust than the Euclidean distance in terms of measuring similarity between objects as data grows in dimensionality \cite{Aggarwal2001}. %(curse of dimensionality)
Those kernel matrices for the Swiss data are compared in Figure \ref{fig:k_matrix_laplacian_comp}.

@@

% gefcom final case
\subsection{GEFCom2014}
The following subsection compares our kernel quantile regression against the price and load track entries of the GEFCom2014 competition.
Error measure of the competition was the pinball loss, see Section \ref{metrics}, averaged over the $99$ quantiles, $q \in \{i/100\}_{i=1}^{n=99}$. Backed by the conclusion from the previous subsection we selected the absolute Laplacian and the Gaussian RBF as kernels in our application of KQR.

@@

\begin{figure}
    \includegraphics[width=\textwidth]{images/cv_scatter.png}
    \label{fig:cv_scatter}
    \caption{Cross validation Gaussian RBF kernel task 4 GEFCom2014 price}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\linewidth]{images/price_task_4_gaussian_rbf.png}
    \caption[Prediction price track task 4, Gaussian RBF kernel]{Price 90\% confidence interval task 4. Electricity price probabilistic forecast for the $4^{\text{th}}$ July $2013$. The black line is the observed path for the price. The $90\%$ confidence interval bands are plotted in green. Lower and upper red lines denote the $95\%$ and $5\%$ quantile forecast respectively}
    % \Description{}
    \label{fig:price_task_4_gaussian_rbf}
\end{figure}

@@

\begin{figure*}[!ht]
    \centering
    \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/load_task_9_laplacian.png}}
    \caption[Prediction load track task 9, Laplacian kernel]{Load 90\% confidence interval task 9 using KQR Laplacian. The black line is the observed path for the load. The 90\% confidence interval bands are plotted in green. Lower and upper red lines denote the 95\% and 5\% quantile forecast respectively}
    \label{fig:load_task_9}
\end{figure*}

\begin{figure*}[!ht]
    \centering
    \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/sub_boxplot_task_9_laplacian_.png}}
    \caption{Boxplot for first two days of probabilistic forecast task 9 using KQR Laplacian}
    \label{fig:boxplot_load_task_9}
\end{figure*}

>>>>

The resulting RMSE on task 1 is 30.59.
What can be concluded, is that multiple linear regression is capable of catching the daily seasonality. Nevertheless, it cannot catch the range of the price series properly.

\subsection{Trigonometric seasonality Box-Cox transformation ARMA errors trend and seasonal components}
Next, we tried with the autoregressive approach. Unfortunately, AR, ARIMA and SARIMA models did not perform as expected, their output was slightly better than the one of linear regression. This is probably due to the fact that, the data considered entails two kinds of seasonalities, while ARIMA models can only handle one at a time. We remind the reader, that the electricity load time series involves both daily and weekly seasonalities. Hence, the need for a more advanced time series model. The Tbats \cite{de2011forecasting} model is a forecasting method capable of handling complex patterns in the data. Its name stands for trigonometric seasonality, Box-Cox transformation, ARMA errors, trend and seasonal components. 
Tbats forecast is visualized in Figure \ref{fig:tbats_price}, meanwhile its RMSE on task 1 is 15.08.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/tbats_price.png}
    \caption{Tbats prediction}
    \label{fig:tbats_price}
\end{figure}
From the plot we see that Tbats is capable of catching the lows and average trend, conversely it has some difficulties handling the price peaks.
\subsection{Prophet}
Following, the prophet model has been considered. 
We get started by considering the base implementation. In such setting, prophet takes as input the time series object and learns its data generating process.
This method achieves on task 1 a RMSE of 23.96, its prediction is visualized in Figure \ref{fig:prophet_price_1}.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/prophet_price_1.png}
    \caption{Prophet prediction}
    \label{fig:prophet_price_1}
\end{figure}
What can be seen is that prophet correctly models the average trend but does not model peaks and lows precisely. 
Next, a more complex model was trained. We added the weather temperature, the square of it and the categorical variable for holidays effect as regressors. Furthermore, we also applied a log transformation to the dependent variables. Doing so, RMSE on task 1 went down to 10.29. Forecast is visualised in Figure \ref{fig:prophet_price2}.
% , moreover figure \ref{fig:prophet_price2.1} and figure \ref{fig:prophet_price2.2} break down the trend and the seasonalities respectively.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/prophet_price2.png}
    \caption{Prophet model\_2 prediction}
    \label{fig:prophet_price2}
\end{figure}

@@

\subsection{K-nearest neighbours}
Afterwards, K-nearest neighbours has been considered. In doing so, we cross validated the number of neighbours to get the best model instance. The forecast is visualised in Figure \ref{fig:knn_price}, RMSE on task 1 is 12.54.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/knn_price.png}
    \caption{K-nearest neighbours regression}
    \label{fig:knn_price}
\end{figure}
What it can be said is that, K-nearest neighbours is capable of predicting load well by averaging past data.

\subsection{Support vector regression}
In applying support vector regression we used gridsearch crossvalidation to search for the best regularisation parameter $C$. Support vector regression achieves on task 1 an RMSE of 23.24, for the prediction see Figure \ref{fig:svr_price}.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/svr_price.png}
    \caption{Support vector regression prediction}
    \label{fig:svr_price}
\end{figure}
Visually, we see that the SVR performs similar to multiple linear regression, as expected. Like multiple linear regression, SVR can model the daily seasonality but the point prediction is off in terms of highs and lows.

\subsection{Long short term memory}\label{sec:lstm point}
We used the \href{https://pytorch.org}{torch} library in order to code our LSTM regressor.
Various hyperparameters combinations were tried during the tuning phase. The final architecture we set on follows
\begin{itemize}
    \item hidden\_size= 64
    \item num\_layers= 2
    \item output\_size= 1
    \item num\_epochs= 30
    \item learning\_rate= 0.001
    \item batch\_size= 32
    \item window\_size= 24
\end{itemize}
LSTM forecast is reported in Figure \ref{fig:lstm_price}, it achieves on task 1 a RMSE of 9.1782
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/lstm_price.png}
    \caption{Long short term memory prediction}
    \label{fig:lstm_price}
\end{figure}

\subsection{Kernel ridge regression}
Subsequently, kernel ridge regression was considered. The kernel considered is the radial basis Gaussian function.
Cross validation was carried jointly over the RBF kernel bandwith and the regularisation constant.
The RMSE achieved on task 1 is 9.86, Figure \ref{fig:krnridge_price} reports the prediction.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/krnridge_price.png}
    \caption{Kernel ridge prediction}
    \label{fig:krnridge_price}
\end{figure}
We can observe that, kernel ridge regression accurately models the electricity time series.

\subsection{Kernel support vector regression}
The last model we considered in this setting was the kernel support vector regression.
RMSE achieved with this method on task 1 is 9.10, forecast is reported in Figure \ref{fig:krnsvr_price}.

@@

\subsection{Results}
This section reports the tables comparing the considered methods' scores.
% in the context of electricity load forecasting.

@@

% quantile regressors
\subsection{Quantile regressors comparison}
Using the load data from \href{https://www.energy-charts.info/index.html?l=en&c=DE}{energy charts} for Germany and Switzerland, we proceeded to compare between quantile regression algorithms. In this study, we trained our models on the entire 2021 data and then tested them and measured their score on the 2022 data.
Notice, for kernel quantile regression (KQR), the kernel of choice in this setting is the Absolute Laplacian. Additionally notice, the loss function utilized in this section is the normalized pinball loss. 
% normalized by the magnitude of the average load of each country.
Here, we built two models. In the first, the national load is forecasted by taking as predictor the following variables
\begin{itemize}
    \item Weather temperature
    \item Wind speed
\end{itemize}
Results for Germany are reported in table \ref{tab:energy_chart_de} and figure \ref{fig:DE_load_CI} while results for Switzerland can be found in table \ref{tab:energy_chart_ch} and figure \ref{fig:CH_load_CI}.

@@

    \begin{figure}[!ht]
        \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/DE_load_CI.png}}
        \caption[Probabilistic forecast for load in Germany]{Load 90\% confidence interval for Germany Energy charts (2022) data using KQR Absolute Laplacian. The black line is the observed path for the load. The 90\% confidence interval bands are plotted in green. Lower and upper red lines denote the 95\% and 5\% quantile forecast respectively}
        \label{fig:DE_load_CI}
    \end{figure}

    \begin{figure}[!ht]
        \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/CH_load_CI.png}}
        \caption[Probabilistic forecast for load in Switzerland]{Load 90\% confidence interval for Switzerland Energy charts data (2022) using KQR Absolute Laplacian. The black line is the observed path for the load. The 90\% confidence interval bands are plotted in green. Lower and upper red lines denote the 95\% and 5\% quantile forecast respectively}
        \label{fig:CH_load_CI}
    \end{figure}

Next, we extended the models to take into account the impact of two additional categorical variables
\begin{itemize}
    \item Is holiday: a binary variable for holidays, where holiday=1 and working day=0
    \item Day of week: an ordinal categorical variable corresponding to the day of the week, e.i.\ Monday=0,$\dots$, Sunday=6
\end{itemize}
Table \ref{tab:energy_chart_de_additional_predictors} reports the model scores on the German data while Table \ref{tab:energy_chart_ch_additional_predictors} is the one corresponding to the Swiss data.

@@

% now comment tables
What can be concluded from this first study is that kernel quantile regression equipped with the Absolute Laplacian kernel outperformed almost always its contenders.

% kernel comparison
\subsection{Kernel function choice}
This section analyzes which kernel function best fits to the characteristics of the load data.
The kernel functions considered are: Gaussian RBF, Absolute Laplacian, Matern 0.5, Matern 1.5, Matern 2.5, Linear, Periodic, Polynomial, Sigmoid, and Cosine. 
Details concerning the hyperparameter selection for the different kernels can be found in \href{https://scikit-learn.org/stable/modules/classes.html#module-sklearn.metrics.pairwise}{sklearn.metrics.pairwise} and \href{https://scikit-learn.org/stable/modules/classes.html#module-sklearn.gaussian_process}{sklearn.gaussian\_process}.
The pool of data for this study has been created by combining \href{https://zenodo.org/records/7907883}{SECURES-Met} data (predictors) \cite{Formayer2023} and the load data from \href{https://www.energy-charts.info/index.html?l=en&c=DE}{energy charts}.
SECURES-Met data consists of historical data up to the end of $2020$ while from 2021 onward, the data consists of forecasts modeled by the European Centre for Medium-Range Weather Forecasts (ECMWF).
Therefore, in this experimental study, we used the whole data of $2020$ as the training set and then tested our kernels on the $2021$ data.
Note that there are two kinds of predictions for data from $2021$ onward, one for each of the emission scenarios RCP$4.5$ and RCP$8.5$. In this study, we considered the more conservative RCP$4.5$ scenario data.

@@

\begin{table}[!ht]
    \centering
    \caption{Pinball loss kernel comparison for load in Switzerland (2021)}
    \label{tab:secures_met_ch}
    \begin{adjustbox}{width=\textwidth}
        \begin{tabular}{lllllllllll}
            \toprule
            Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
            \midrule
            0.1 & \textbf{0.018783} & 0.018988 & 0.019108 & 0.019257 & 0.019547 & 0.019952 & 0.018891 & 0.019654 & 0.021456 & 0.021921 \\
            0.2 & \textbf{0.030441} & 0.030668 & 0.030809 & 0.031028 & 0.031546 & 0.032158 & 0.030683 & 0.031857 & 0.034032 & 0.034629 \\
            0.3 & \textbf{0.038467} & 0.038864 & 0.039050 & 0.039285 & 0.039907 & 0.040657 & 0.038968 & 0.040075 & 0.042944 & 0.043393 \\
            0.4 & \textbf{0.043622} & 0.044186 & 0.044516 & 0.044706 & 0.045286 & 0.046153 & 0.044354 & 0.045506 & 0.048701 & 0.048977 \\
            0.5 & \textbf{0.046160} & 0.046792 & 0.047205 & 0.047450 & 0.048116 & 0.048951 & 0.046956 & 0.047891 & 0.051423 & 0.051896 \\
            0.6 & \textbf{0.045499} & 0.046133 & 0.046824 & 0.047177 & 0.047840 & 0.048667 & 0.046446 & 0.047496 & 0.051292 & 0.051894 \\
            0.7 & \textbf{0.041494} & 0.042044 & 0.042928 & 0.043371 & 0.044104 & 0.044926 & 0.042458 & 0.043565 & 0.047656 & 0.048275 \\
            0.8 & \textbf{0.033837} & 0.034128 & 0.034797 & 0.035325 & 0.036166 & 0.037055 & 0.034290 & 0.035533 & 0.039501 & 0.040007 \\
            0.9 & 0.021883 & \textbf{0.021871} & 0.022431 & 0.022682 & 0.023169 & 0.023730 & 0.022000 & 0.022811 & 0.025561 & 0.026019 \\
            \midrule
            CRPS & \textbf{0.035576} & 0.035964 & 0.036407 & 0.036698 & 0.037298 & 0.038028 & 0.036116 & 0.037154 & 0.040285 & 0.040779 \\
            \bottomrule
    \end{tabular}
\end{adjustbox}
    \end{table}

@@

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Austria (2021)}
\label{tab:secures_met_at}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
        \toprule
        Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
        \midrule
        0.1 & \textbf{0.024365} & 0.024592 & 0.024550 & 0.024611 & 0.024831 & 0.026853 & 0.025744 & 0.026004 & 0.027672 & 0.027816 \\
        0.2 & \textbf{0.040971} & 0.041406 & 0.041413 & 0.041487 & 0.041857 & 0.045007 & 0.043247 & 0.043720 & 0.045899 & 0.045879 \\
        0.3 & \textbf{0.052316} & 0.052969 & 0.052888 & 0.052973 & 0.053449 & 0.057880 & 0.055231 & 0.055446 & 0.058572 & 0.058454 \\
        0.4 & \textbf{0.058286} & 0.059018 & 0.058916 & 0.059078 & 0.059592 & 0.065770 & 0.061844 & 0.062495 & 0.066599 & 0.066335 \\
        0.5 & \textbf{0.060344} & 0.061100 & 0.061319 & 0.061541 & 0.062338 & 0.068197 & 0.063864 & 0.071731 & 0.069761 & 0.069574 \\
        0.6 & \textbf{0.058724} & 0.059507 & 0.059674 & 0.059930 & 0.060709 & 0.065828 & 0.062265 & 0.070269 & 0.067179 & 0.066970 \\
        0.7 & \textbf{0.053148} & 0.054189 & 0.054249 & 0.054372 & 0.054916 & 0.058548 & 0.055830 & 0.063015 & 0.059807 & 0.059419 \\
        0.8 & \textbf{0.042740} & 0.043368 & 0.043408 & 0.043510 & 0.043881 & 0.046017 & 0.044384 & 0.049813 & 0.047078 & 0.046662 \\
        0.9 & \textbf{0.026430} & 0.026583 & 0.026781 & 0.026817 & 0.026908 & 0.027050 & 0.026471 & 0.030279 & 0.028031 & 0.027986 \\
        \midrule
        CRPS & \textbf{0.046369} & 0.046970 & 0.047022 & 0.047146 & 0.047609 & 0.051239 & 0.048764 & 0.052530 & 0.052289 & 0.052122 \\
        \bottomrule
    \end{tabular}
\end{adjustbox}
\end{table}
From our tables, it can be concluded that the Absolute Laplacian kernel is the one fitting best to the characteristics of load data.
Additionally, we can conclude that our results are in line with the ones published in \cite{he2017short}. In that study, similarly to what we did in this subsection, the authors carried out a comparitive study concerning the choice of kernels in KQR. Nevertheless notice, that the set of kernel we considered in our study is larger than the one presented in \cite{he2017short}.
Their paper showed evidence of the superiority of the Gaussian RBF among their set of kernel functions. Analogously, we can see from Tables \ref{tab:secures_met_de}, \ref{tab:secures_met_ch} and \ref{tab:secures_met_at} that the Matern kernels are the best in terms of pinball loss.
The Periodic equipped with period $p=24$ shows good performance. 
After those kernels, we have the Linear and Polynomial kernels.
The worst among all kernels considered are the Cosine and the Sigmoid.
% , which is better suited for binary classification tasks. 
Finally, given that the features dimension is greater than one we have that the Absolute Laplacian and the Matern 0.5 kernels differ. The former kernel is better than the latter and this comes from their distance function. This is because the Manhattan distance is more robust than the Euclidean distance in terms of measuring similarity between objects as data grows in dimensionality \cite{Aggarwal2001}. %(curse of dimensionality)
Those kernel matrices for the Swiss data are compared in Figure \ref{fig:k_matrix_laplacian_comp}.

@@

% gefcom final case
\subsection{GEFCom2014}
The following subsection compares our kernel quantile regression against the price and load track entries of the GEFCom2014 competition.
Error measure of the competition was the pinball loss, see Section \ref{metrics}, averaged over the $99$ quantiles, $q \in \{i/100\}_{i=1}^{n=99}$. Backed by the conclusion from the previous subsection we selected the Absolute Laplacian and the Gaussian RBF as kernels in our application of KQR.

@@

\begin{figure}
    \includegraphics[width=\textwidth]{images/cv_scatter.png}
    \label{fig:cv_scatter}
    \caption{Cross validation price track task 4, Gaussian RBF kernel}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\linewidth]{images/price_task_4_gaussian_rbf.png}
    \caption[Prediction price track task 4, Gaussian RBF kernel]{Price 90\% confidence interval task 4 using KQR Gaussian RBF. Electricity price probabilistic forecast for the $4^{\text{th}}$ July $2013$. The black line is the observed path for the price. The $90\%$ confidence interval bands are plotted in green. Lower and upper red lines denote the $95\%$ and $5\%$ quantile forecast respectively}
    % \Description{}
    \label{fig:price_task_4_gaussian_rbf}
\end{figure}

@@

\begin{figure*}[!ht]
    \centering
    \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/load_task_9_laplacian.png}}
    \caption[Prediction load track task 9, Absolute Laplacian kernel]{Load 90\% confidence interval task 9 using KQR Absolute Laplacian. The black line is the observed path for the load. The 90\% confidence interval bands are plotted in green. Lower and upper red lines denote the 95\% and 5\% quantile forecast respectively}
    \label{fig:load_task_9}
\end{figure*}

\begin{figure*}[!ht]
    \centering
    \makebox[\linewidth]{\includegraphics[width = 1.5\textwidth]{images/sub_boxplot_task_9_laplacian_.png}}
    \caption{Boxplot for first two days of probabilistic forecast task 9 using KQR Absolute Laplacian}
    \label{fig:boxplot_load_task_9}
\end{figure*}
